libgEDAColor(1)                 0.4.0-20190401                 libgEDAColor(1)



NAME
       libgEDAColor - The GPL Electronic Design Automation Color Library

DESCRIPTION
       libgEDAColor  is an extension library used in the gEDA suite to coordi-
       nate the mapping of color codes used in gEDA data files to actual  col-
       ors  used  for  output devices based on user configuration preferences.
       libgEDAColor provides functions for parsing gEDA scheme color-map  data
       and  API  functions  for applications to access color information. This
       manual page explains the user aspects of using libgEDAColor ,  specifi-
       cally,  modifying  color map files. For information on libgEDAColor API
       see libgedacolor(3)

CONFIGURATION
       Predefined color map files are installed with the geda-gaf  suite.  The
       files are really Scheme scripts that are either executed or sourced and
       accordingly the files are located  in  the  GEDADATARC  directory,  see
       libgeda(1).  The files names are:

              display-colormap-bw

              display-colormap-custom

              display-colormap-darkbg

              display-colormap-lightbg

              print-colormap-lightbg

              print-colormap-darkbg

       The  particular  dialect of Scheme used by Libgedacolor is GNU's Guile.
       While it is required for Guile to be installed on the host  system  for
       Libgedacolor  to process these files, it is not a requirement that gEDA
       applications initialize or even be running  Guile.   Libgedacolor  does
       not  initiate  the  loading  of  "rc"  files.  Instead, application can
       request that a initialization file be processed. Alternatively,  appli-
       cation  rc  files  can  reference  the  color map files. Examples of rc
       entries in applications might look like:

              (primitive-load  (build-path   geda-rc-path   "display-colormap-
              darkbg"))

              (load (build-path geda-rc-path "display-colormap-darkbg"))

              (load ("$HOME/etc/gEDA/display-colormap-darkbg"))

FILE FORMAT
       Each  color  map  file  contains one or more functions that pass a list
       containing color information as arguments. The color maps file normally
       only reference three functions:

              display-color-map

              display-outline-color-map

              print-color-map

       The  argument  list  to  each of these functions is a list of key value
       pairs in the form ("key" "color"). "key" must be a  string  name  of  a
       recognized  component  or  artifact. Provided color map files contain a
       complete list of all recognized keys, but all keys need not be present.
       The color can be a hex string representation of the color or #f to dis-
       able color for the corresponding key entry.

DOCUMENTATION
       The gEDA-gaf suite utilizes Doxygen for  generating  source  documenta-
       tion.  By  default  this  documentation  is  not  generated and must be
       enabled via the configuration option --with-doxygen. When enabled,  the
       documentation  is  then  built  in the source tree using "make doxygen"
       from the top of the source. To only generate source  documentation  for
       libgEDAColor use "make doxygen" from within the libgEDAColor directory.
       Note that the configure script can also set the configuration to allows
       generating  the  source  documentation out of the source tree using the
       --with-doxygen-out   option.   For   example   using    --with-doxygen-
       out=/tmp/geda-gaf  will  cause the resulting documentation to be gener-
       ated in the "/tmp/geda-gaf" directory. The  target  directory  will  be
       created  if  it does not already exist. It is not necessary to use both
       doxygen options, using --with-doxygen-out automatically enables --with-
       doxygen.   The  Doxygen  configuration  is set to produce both HTML and
       latex. Other formats are possible, see the  Doxygen  documentation  for
       details.

AUTHORS
       See the "AUTHORS" file included with this library.

COPYRIGHT
       Copyright (C) 2019 gEDA Contributors. License GPLv2+: GNU GPL
       version 2 or later. Please see the "COPYING" file included with this
       program for full details.

       This is free software: you are free to change and redistribute it. There is NO
       WARRANTY; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE, to
       the extent permitted by law.

SEE ALSO
       libgedacolor(3),     libgeda(1),    libgedacairo(1),    libgedathon(1),
       libgedauio(1)

       http://wiki.geda-project.org/geda:documentation.



Libgedacolor(3)                 0.4.0.20171112                 Libgedacolor(3)



NAME
       Libgedacolor - The GPL Electronic Design Automation Color Library


SYNOPSIS
       #include <libgedacolor.h>


DESCRIPTION
       Libgedacolor is an extension library used in the gEDA suite to  coordi-
       nate  the mapping of color codes used in gEDA data files to actual col-
       ors used for output devices based on user configuration preferences...

LINKAGE
   Using pkg-config
       LDFLAGS = pkg-config --libs libgedacolor

   Base library
       if installed from a package

       -lgedacolor

       if built from source

       -L/${prefix}=installed   directory/gEDA/lib   -lgedacolor    (typically
       /usr/local/gEDA/lib)

HEADERS
   Using pkg-config
       pkg-config --cflags libgedacolor

   if installed from a package
       #include <gEDA/libgedacolor.h>

   if built from source
       -I/${prefix}/gEDA/include/libgedacolor

PROTOTYPES
                       void      libgedacolor_init                (int  *argc,
              char **argv);
                       int     geda_color_load_display_scheme  (char *scheme);
                       int     geda_color_load_print_scheme    (char *scheme);
                       void    libgedacolor_release            (void);

                        SCM    geda_color_guile_display_map    (SCM scm_map);
                        SCM    geda_color_guile_outline_map    (SCM scm_map);
                        SCM    geda_color_guile_print_map      (SCM scm_map);

                        SCM     geda_color_guile_map_to_scm      (const  COLOR
              *map);
                       void     geda_color_guile_map_from_scm    (COLOR  *map,
              SCM lst, const char *scheme_proc_name);

                       char    *geda_color_get_color_name        (int   index,
              GArray *map, GError **err);
                        int    geda_color_get_object_default   (char type);

                     GArray   *geda_color_get_display_map      (void);
                     GArray   *geda_color_get_standard_names   (void);
                     GArray   *geda_color_get_outline_map      (void);
                     GArray   *geda_color_get_print_map        (void);

                        int      geda_color_key_get_index         (const  char
              *name);

                       bool     geda_color_utility_decode_rgba   (const   char
              *rgba, guchar *r, guchar *g, guchar *b, guchar *a);
                       char   *geda_color_utility_encode_rgba  (uint8 r, uint8
              g, uint8 b, uint8 a);
                       char   *geda_color_utility_get_hex      (COLOR *c);
                       char    *geda_color_utility_lookup_name   (COLOR   *c1,
              GError **err);
                       char   *geda_color_utility_postscript   (int color);

                       void    geda_color_x11_init             (void);
                       void    geda_color_x11_free             (void);
                       void    geda_color_x11_allocate         (void);
                   GdkColor   *geda_color_x11_color_from_index (int color);
                      COLOR   *geda_color_x11_lookup           (int color);
                       bool    geda_color_x11_get_state        (int color);
                       void    geda_color_x11_set_state        (int color, int
              state);
                       bool    geda_color_x11_enabled          (int index);


AUTHORS
       See the `AUTHORS' file included with this program.


COPYRIGHT
       Copyright (C) 2017 gEDA Contributors. License GPLv2+: GNU GPL
       version 2 or later. Please see the `COPYING' file included with this
       program for full details.

       This is free software: you are free to change and redistribute it.
       There is NO WARRANTY, to the extent permitted by law.


SEE ALSO
       libgedacolor(1),    libgeda(1),    libgedacairo(1),     libgedathon(1),
       libgedauio(1)

       API documentation for libgedacolor can be generated using Doxygen using
       'Make doxygen' in the libgedacolor source directory.



gEDA Project                   November 12, 2017               Libgedacolor(3)
